---
title: "NSF funding in Databrary projects"
author: "Rick Gilmore"
output: html_document
date: "`r Sys.Date()`"
params:
  max_vol_id: 1626
  vb: TRUE
  import_saved: TRUE
  eval_test: FALSE
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

This document describes the process for providing full funding data for projects shared on Databrary that list the U.S. National Science Foundation as a funding source [^1].

Databrary stores a funding name, and a text field with the award ID, but it does not include the project title, funding amount, or other data related to an award.
That data is available, however, from the NSF.

This document uses the `databraryapi` (soon to be moved to the `databrary/databraryr` package to extract information about the projects (volumes) that list NSF as a funder and then pulls additional data from the NSF's data via the NSF API.

Most of the work is done via functions listed in `R/functions.R`.

```{r}
source("R/functions.R")
```

## Preliminary testing

Information about the preliminary testing and development of these functions can be found in [prep-work.html](prep_work.html).

## Report on all Databrary volumes

### Databrary volumes that mention NSF

To query Databrary for the volumes that mention an NSF award, we run the following.

```{r, eval=FALSE, message=FALSE, warning=FALSE}
db_w_nsf <-
  purrr::map(1:params$max_vol_id,
             get_vol_awards,
             funder_str = "NSF",
             .progress = "Databrary vols w/ NSF:") |> purrr::list_rbind() |>
  add_clean_nsf_award_id()
```

The above uses the `get_vol_awards()` function and the `funder_str` parameter to select award information that lists NSF. Then, the NSF award IDs are cleaned to match the NSF format with `add_clean_nsf_award_id()`.

This takes several moments, so for this report, we import a previously saved file with this data.

```{r import-saved-db-nsf, eval=params$import_saved}
db_nsf <- readr::read_csv("csv/databrary-vols-w-nsf-funding-all.csv", show_col_types = FALSE)
```

Then, we can start to visualize the data.

```{r show-table-databrary-vols-listing-nsf}
db_nsf |>
  dplyr::select(vol_id, award_id, award) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material() |>
  kableExtra::scroll_box(width = "600px", height = "300px")
```

### Databrary volumes with matching NSF data

To re-generate a data frame with the Databrary volumes for which we are able to extract more details about the NSF funding from the NSF itself, we run

```{r, eval=FALSE}
summarize_mult_vol_nsf_awards(1:params$max_vol_id, vb = TRUE)
```

This takes several moments, so for this report, we import a previously saved file.

```{r import-saved, eval=params$import_saved}
nsf <- readr::read_csv("csv/databrary-nsf-funding-details-all.csv", show_col_types = FALSE)
```

Now, we can begin to visualize this, as well:

```{r show-table-nsf-info}
nsf <- nsf |>
   dplyr::filter(!is.na(piLastName), !is.na(piFirstName), !is.na(award_id))
 
nsf |>
  dplyr::select(piLastName, piFirstName, award_id, date, title, vol_id, fundsObligatedAmt) |>
  dplyr::arrange(piLastName, award_id, vol_id) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material() |>
  kableExtra::scroll_box(width = "600px", height = "300px")
```

### Visualize

```{r nsf-award-histogram-all, fig.cap="Histogram of NSF awards for all Databrary volumes."}
nsf |>
  dplyr::mutate(award_amt = as.numeric(fundsObligatedAmt)) |>
  ggplot2::ggplot() +
  ggplot2::aes(award_amt) +
  ggplot2::geom_histogram(bins=10)
```

There are $n=$ `r dim(db_nsf)[1]` Databrary volumes that list NSF as a funder.

These represent $n=$ `r db_nsf$award_id |> na.omit() |> unique() |> length()` unique NSF awards.

Of these, we were able to extract data from the NSF API for $n=$ `r nsf$award_id |> na.omit() |> unique() |> length()` NSF awards.

The following volumes do not have matching NSF awards.

```{r}
db_not_found_in_nsf <- !(db_nsf$vol_id %in% nsf$vol_id)

db_nsf |>
  dplyr::filter(db_not_found_in_nsf) |>
  dplyr::select(vol_id, award) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material() |>
  kableExtra::scroll_box(width = "600px", height = "200px")
```

A next step would be to identify the PIs on these volumes and contact them to rectify the issue.

## Cleanup

```{r}
databraryapi::logout_db()
```

[^1]: In a form that permits us to query the NSF API.
