---
title: "NSF Projects on Databrary"
output: html_document
date: "`r Sys.Date()`"
params:
  max_vol_id: 1600
  vb: FALSE
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

This document describes the process for providing full funding data for projects shared on Databrary that list the U.S. National Science Foundation as a funding source.

Databrary stores a funding name, and a text field with the award ID, but it does not include the project title, funding amount, or other data related to an award.
That data is available, however, from the NSF.

This document uses the `databraryapi` package to extract information about the projects (volumes) that list NSF as a funder and then pulls additional data from the NSF's data via the NSF API.

Most of the work is done via functions listed in `R/functions.R`.

```{r}
source("R/functions.R")
```

## Preliminary testing

### Extract NSF-funded projects from Databrary

For efficiency reasons, we test the workflow by limiting the number of Databrary volumes queried.

The following chunks have been disabled (`eval = FALSE`).

```{r retrieve-nsf-vol1-200, eval=FALSE}
vols_1_200 <- get_multiple_vol_nsf_awards(1:200)
```

```{r print-vol1-200, eval=FALSE}
vols_1_200 |>
  dplyr::select(vol_id, award) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material()
```

### Extract details from NSF

```{r, eval=FALSE}
vols_1_200_clean <- add_clean_nsf_award_id(vols_1_200)
```

```{r get-nsf-award-info-vol1-200, eval=FALSE}
nsf_vols_1_200 <- get_mult_nsf_awards(vols_1_200_clean$award_id)
```

```{r print-nsf-vol1-200, eval=FALSE}
nsf_vols_1_200 |>
  dplyr::select(-agency) |>
  dplyr::arrange(awardeeName, desc(date)) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material() |>
  kableExtra::scroll_box(width = "600px", height = "300px")
```

### Save data

```{r save-csvs, eval=FALSE}
readr::write_csv(nsf_vols_1_200, "csv/databrary-nsf-funding-details.csv")
readr::write_csv(vols_1_200_clean, "csv/databrary-vols-w-nsf-funding.csv")
```

### Visualize data

```{r nsf-award-histogram, fig.cap="Histogram of NSF awards for selected Databrary volumes", eval=FALSE}
nsf_vols_1_200 |>
  dplyr::mutate(award_amt = as.numeric(fundsObligatedAmt)) |>
  ggplot2::ggplot() +
  ggplot2::aes(award_amt) +
  ggplot2::geom_histogram(bins=10)
```

## Full dataset

### Extract NSF-funded projects from Databrary

```{r get-all-db-vols-w-nsf}
db_nsf <- get_multiple_vol_nsf_awards(1:params$max_vol_id, vb = params$vb)
db_nsf <- add_clean_nsf_award_id(db_nsf)

db_nsf |>
  dplyr::select(vol_id, award) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material() |>
  kableExtra::scroll_box(width = "600px", height = "300px")
```

### Extract details from NSF

```{r get-nsf-details-for-all}
nsf <- get_mult_nsf_awards(db_nsf$award_id, vb = params$vb)

nsf |>
  dplyr::select(-agency) |>
  dplyr::arrange(awardeeName, desc(date)) |>
  knitr::kable(format = 'html') |>
  kableExtra::kable_material() |>
  kableExtra::scroll_box(width = "600px", height = "300px")
```
### Save data

```{r save-csvs-all}
readr::write_csv(nsf, "csv/databrary-nsf-funding-details-all.csv")
readr::write_csv(db_nsf, "csv/databrary-vols-w-nsf-funding-all.csv")
```

### Visualize

```{r nsf-award-histogram-all, fig.cap="Histogram of NSF awards for all Databrary volumes as of `r Sys.Date()`"}
nsf |>
  dplyr::mutate(award_amt = as.numeric(fundsObligatedAmt)) |>
  ggplot2::ggplot() +
  ggplot2::aes(award_amt) +
  ggplot2::geom_histogram(bins=10)
```

There are $n=$ `r dim(db_nsf)[1]` shared projects on Databrary that list NSF funding, with $n=$ `r dim(db_nsf$award_id)` unique NSF awards.
Of these $n=$ `r length(unique(na.omit(nsf$id))` list NSF funding in a form that permits us to query the NSF API.
The award amounts range from `r min(as.numeric(na.omit(nsf$fundsObligatedAmt)))` to `r max(as.numeric(na.omit(nsf$fundsObligatedAmt)))`, with a mean of `r mean(as.numeric(na.omit(nsf$fundsObligatedAmt)))` and a median of `r median(as.numeric(na.omit(nsf$fundsObligatedAmt)))`.

## (TODO) Merge NSF and Databrary info

[^1]: In a form that permits us to query the NSF API.
